Overview of the eHealth Knowledge Discovery Challenge at IberLEF 2021

### 2021-06-22 paper/paper.tex

Staying up-to-date on information about topics of interest is crucial in technical or scientific domains.
For this purpose, specialists rely on a combination of curated soruces (e.g., domain-specific repositories like arxiv, bioarxiv, semantic scholar) and technologies for search and recommendation (e.g., google scholar).
These resources significantly improve the experience of collecting and consuming large amounts of relevant information on a specific topic.
Tools like Connected Papers~\cite{} and Papers with Code~\cite{} are one step beyond the indexing of documents, providing summarised and structured representations of the content in a collection of documents.
However, it remains an open problem to automatically combine, summarise, and present the relevant information in a collection of documents in a semantic structure~(e.g., a knowledge graph) that allows a specialist to quickly grasp the essential concepts of a specific knowledge field.

A potential solution to this problem would require methods to automatically detect in natural language the most relevant concepts and the factual statements in which they are related, possibly normalise them into well-established taxonomies and classifications, and store them in computational data structures where they can linked with related concepts, e.g., knowledge graphs.
The first step of this process, i.e., the detection of relevant concepts and semantic relations in text, is already a challenging computational task, given the complexity and variability of natural language.
To encourage research and development in this area, several academic competitions have been organised through the years by organizations such as CLEF, SEMEVAL, and more recently, IBERLEF.

In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1900 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is constructed.
Based on this annotation model, two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
A shared annotation campaign was organized, where a total of 9 participants presented 10 different systems with varied levels of performance.

The eHealth-KD task focuses on cross-domain, multi-lingual and low-resource solutions. This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
A succesful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.

>>>>

Staying up-to-date on information about topics of interest is crucial in technical or scientific domains.
For this purpose, specialists rely on a combination of curated sources (e.g., domain-specific repositories like arxiv, bioarxiv, semantic scholar) and technologies for search and recommendation (e.g., google scholar).
These resources significantly improve the experience of collecting and consuming large amounts of relevant information on a specific topic.
Tools like Connected Papers~\cite{} and Papers with Code~\cite{} are one step beyond the indexing of documents, providing summarised and structured representations of the content in a collection of documents.
However, it remains an open problem to automatically combine, summarise, and present the relevant information in a collection of documents in a semantic structure~(e.g., a knowledge graph) that allows a specialist to quickly grasp the essential concepts of a specific knowledge field.

A potential solution to this problem would require methods to automatically detect in natural language the most relevant concepts and the factual statements in which they are related, possibly normalise them into well-established taxonomies and classifications, and store them in computational data structures where they can linked with related concepts, e.g., knowledge graphs.
The first step of this process, i.e., the detection of relevant concepts and semantic relations in text, is already a challenging computational task, given the complexity and variability of natural language.
To encourage research and development in this area, several academic competitions have been organised through the years by organisations such as CLEF, SEMEVAL, and more recently, IBERLEF.

In this context, the eHealth Knowledge Discovery Challenge is designed to foster the development of automatic knowledge discovery systems for natural language sentences in a cross-domain and multi-lingual setting.
Concretely, a token-level annotation model of 4 entities and 13 semantic relations is defined, and a corpus of more than 1500 sentences from different factual sources~(i.e., Spanish Medline articles, Spanish Wikinews articles, and English biomedical preprints related to COVID-19) is annotated.
Two computational tasks are defined: the detection of multi-span, non-contiguous, and potentially overlapping named entities; and the detection of semantic relations between them.
A shared annotation campaign was organised, where a total of 9 participants presented 10 different systems with varied levels of performance.

The eHealth-KD task focuses on cross-domain, multi-lingual and low-resource solutions. This setting presents a significant challenge to existing state-of-the-art methods, which often rely on large amounts of training data.
A successful approach to the eHealth-KD must leverage transfer learning across different domains and languages, since the vast majority of the training examples are provided in Spanish language and from the Medline domain, while only a small development set is available in the remaining settings.
With this added complexity, we expect to encourage solutions that can be deployed in low-resource environments, where is unfeasible to train large language models over longs periods of time.
